From Precipitation to Prediction: Integrating ConvLSTM Models for Comprehensive River Runoff Forecasting

### 2024-03-20 paper/paper.qmd
update newest
most recent images added

---
title: "From Precipitation to Prediction: Integrating ConvLSTM Models for Comprehensive River Runoff Forecasting"
format:
    agu-pdf:
        keep-tex: true
    agu-html: default
author:
  - name: Florian Börgel
    affiliations: 
      - ref: IOW
    orcid: 0000-0003-2402-304X
    email: florian.boergel@io-warnemuende.de
    corresponding: true

@@

@fig-PerformanceNeuralNetworkRunoff shows the perfomance of the model using the test dataset. The predicted total river runoff for the Baltic Sea is closely matching the original data. Zooming in on the largest individual rivers (lower panels) it can be seen that that also the prediction of the inidivual rivers is close to the original data.

![Figure ..](images/paste-1.png){#fig-PerformanceNeuralNetworkRunoff}

@@

![Figure ...](images/paste-4.png){#fig-statistical-evaluationNN}

@@

![](images/paste-5.png){#fig-by15}

![](images/paste-6.png)

>>>>

---
git pul---
title: "From Precipitation to Prediction: Integrating ConvLSTM Models for Comprehensive River Runoff Forecasting"
format:
    agu-pdf:
        keep-tex: true
    agu-html: default
author:
  - name: Florian Börgel
    affiliations: 
      - ref: IOW
    orcid: 0000-0003-2402-304X
    email: florian.boergel@io-warnemuende.de
    corresponding: true

@@

@@

![](images/paste-13.png)

@fig-PerformanceNeuralNetworkRunoff shows the performance of the model using the test dataset. The predicted total river runoff for the Baltic Sea is closely matching the original data. Zooming in on the largest individual rivers (lower panels) it can be seen that that also the prediction of the inidivual rivers is close to the original data.

![](images/paper_total_river_runoff.png)

@@

![](images/paste-9.png)

![](images/paste-12.png)
